---
output: github_document
bibliography: inst/references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# didimputation

<!-- badges: start -->
<!-- badges: end -->

The goal of didimputation is to estimate TWFE models without running into the problem of staggered treatment adoption. 

## Installation

You can install didimputation from github with:

``` r
devtools::install_github("kylebutts/didimputation")
```

### TWFE vs. DID Imputation Example

I will load example data from the package and plot the average outcome among the groups. Here is one unit's data:

```{r load-data, code_folding=TRUE,}

library(tidyverse)
library(didimputation)
library(fixest)

# Load theme
source("https://raw.githubusercontent.com/kylebutts/templates/master/ggplot_theme/theme_kyle.R")

# Load Data from did2s package
data("df_het", package="did2s")
```

Here is a plot of the average outcome variable for each of the groups:

```{r plot-df-het, fig.width=8, fig.height=4, fig.cap="Example data with heterogeneous treatment effects", code_folding=TRUE, layout="l-body-outset"}
# Plot Data 
df_avg <- df_het %>% 
  group_by(group, year) %>% 
  summarize(dep_var = mean(dep_var), .groups = 'drop')

# Get treatment years for plotting
gs <- df_het %>% 
  filter(treat == TRUE) %>% 
  pull(g) %>% unique()
	
	
ggplot() + 
	geom_line(data = df_avg, mapping = aes(y = dep_var, x = year, color = group), size = 1.5) +
	geom_vline(xintercept = gs - 0.5, linetype = "dashed") + 
	theme_kyle(base_size = 16) +
	theme(legend.position = "bottom") +
	labs(y = "Outcome", x = "Year", color = "Treatment Cohort") + 
	scale_y_continuous(expand = expansion(add = .5)) + 
	scale_color_manual(values = c("Group 1" = "#d2382c", "Group 2" = "#497eb3", "Group 3" = "#8e549f")) 
```


### Estimate DID Imputation

First, lets estimate a static did:

```{r static}

# Static
static <- did_imputation(data = df_het, yname = "dep_var", gname = "g", tname = "year", idname = "unit")

static

```

This is very close to the true treatment effect of `r df_het %>% filter(treat == 1) %>% summarize(att = mean(te + te_dynamic)) %>% pull(att)`.

Then, let's estimate an event study did:

```{r event-study}

# Event Study
es <- did_imputation(data = df_het, yname = "dep_var", gname = "g",
			   tname = "year", idname = "unit", 
			   # event-study
			   horizon=TRUE, pretrends = -5:-1)

es

```

And plot the results:

```{r plot-es, fig.width=8, fig.height=4, fig.cap="Event-study plot with example data", code_folding=TRUE, layout="l-body-outset"}

pts <- es %>%
	select(rel_year = term, estimate, std.error) %>%
    mutate(
        ci_lower = estimate - 1.96 * std.error,
        ci_upper = estimate + 1.96 * std.error,
        group = "DID Imputation Estimate",
        rel_year = as.numeric(rel_year)
    ) %>%
    filter(rel_year >= -8 & rel_year <= 8) %>% 
    mutate(rel_year = rel_year + 0.1)

te_true <- df_het %>%
    # Keep only treated units
    filter(g > 0) %>%
    group_by(rel_year) %>%
    summarize(estimate = mean(te + te_dynamic)) %>%
	  mutate(group = "True Effect") %>%
    filter(rel_year >= -8 & rel_year <= 8) %>% 
    mutate(rel_year = rel_year)

pts <- bind_rows(pts, te_true)

max_y <- max(pts$estimate)

ggplot() +
    # 0 effect
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    # Confidence Intervals
    geom_linerange(data = pts, mapping = aes(x = rel_year, ymin = ci_lower, ymax = ci_upper), color = "grey30") +
    # Estimates
    geom_point(data = pts, mapping = aes(x = rel_year, y = estimate, color = group), size = 2) +
    # Label
    geom_label(data = data.frame(x = -0.5 - 0.1, y = max_y + 0.25, label = "Treatment Starts ▶"), label.size=NA,
               mapping = aes(x = x, y = y, label = label), size = 5.5, hjust = 1, fontface = 2, inherit.aes = FALSE) +
    scale_x_continuous(breaks = -8:8, minor_breaks = NULL) +
    scale_y_continuous(minor_breaks = NULL) +
    scale_color_manual(values = c("DID Imputation Estimate" = "steelblue", "True Effect" = "#b44682")) +
    labs(x = "Relative Time", y = "Estimate", color = NULL, title = NULL) +
    theme_kyle(base_size = 16) +
    theme(legend.position = "bottom")

```


### Comparison to TWFE

```{r plot-compare, fig.width=8, fig.height=4, fig.cap="TWFE and Two-Stage estimates of Event-Study", code_folding=TRUE, layout="l-body-outset"}

# TWFE
twfe <- fixest::feols(dep_var ~ i(rel_year, ref=c(-1, Inf)) | unit + year, data = df_het) %>%
	broom::tidy() %>%
    filter(str_detect(term, "rel_year::")) %>%
	select(rel_year = term, estimate, std.error) %>%
    mutate(
        rel_year = as.numeric(str_remove(rel_year, "rel_year::")),
        ci_lower = estimate - 1.96 * std.error,
        ci_upper = estimate + 1.96 * std.error,
        group = "TWFE Estimate"
    ) %>%
    filter(rel_year <= 8 & rel_year >= -8) %>% 
    mutate(rel_year = rel_year - 0.1)

# Add TWFE Points
both_pts <- pts %>% mutate(
		group = if_else(group == "Estimated Effect", "DID Imputation Estimate", group)
	) %>% 
	bind_rows(., twfe)


ggplot() +
    # 0 effect
    geom_hline(yintercept = 0, linetype = "dashed") +
    geom_vline(xintercept = -0.5, linetype = "dashed") +
    # Confidence Intervals
    geom_linerange(data = both_pts, mapping = aes(x = rel_year, ymin = ci_lower, ymax = ci_upper), color = "grey30") +
    # Estimates
    geom_point(data = both_pts, mapping = aes(x = rel_year, y = estimate, color = group), size = 2) +
    # Label
    geom_label(data = data.frame(x = -0.5 - 0.1, y = max_y + 0.25, label = "Treatment Starts ▶"), label.size=NA,
               mapping = aes(x = x, y = y, label = label), size = 5.5, hjust = 1, fontface = 2, inherit.aes = FALSE) +
    scale_x_continuous(breaks = -8:8, minor_breaks = NULL) +
    scale_y_continuous(minor_breaks = NULL) +
    scale_color_manual(values = c("DID Imputation Estimate" = "steelblue", "True Effect" = "#b44682", "TWFE Estimate" = "#82b446")) +
    labs(x = "Relative Time", y = "Estimate", color = NULL, title = NULL) +
    theme_kyle(base_size = 16) +
    theme(legend.position = "bottom")

```




# References



