---
output: github_document
bibliography: inst/references.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# didimputation

<!-- badges: start -->
<!-- badges: end -->

The goal of didimputation is to estimate TWFE models without running into the problem of staggered treatment adoption. 

## Installation

You can install didimputation from github with:

``` r
devtools::install_github("kylebutts/didimputation")
```

### TWFE vs. DID Imputation Example

I will load example data from the package and plot the average outcome among the groups. Here is one unit's data:

```{r load-data, code_folding=TRUE,}
library(didimputation)
library(fixest)
library(ggplot2)

# Load Data from did2s package
data("df_het", package = "didimputation")
setDT(df_het)
```

Here is a plot of the average outcome variable for each of the groups:

```{r plot-df-het, fig.width=8, fig.height=4, fig.cap="Example data with heterogeneous treatment effects", code_folding=TRUE, layout="l-body-outset"}
# Plot Data
df_avg <- df_het[,
  .(dep_var = mean(dep_var)),
  by = .(group, year)
]

# Get treatment years for plotting
gs <- df_het[treat == TRUE, unique(g)]

ggplot() +
  geom_line(data = df_avg, mapping = aes(y = dep_var, x = year, color = group), size = 1.5) +
  geom_vline(xintercept = gs - 0.5, linetype = "dashed") +
  theme_minimal(base_size = 16) +
  theme(legend.position = "bottom") +
  labs(y = "Outcome", x = "Year", color = "Treatment Cohort") +
  scale_y_continuous(expand = expansion(add = .5)) +
  scale_color_manual(values = c("Group 1" = "#d2382c", "Group 2" = "#497eb3", "Group 3" = "#8e549f"))
```


### Estimate DID Imputation

First, lets estimate a static did:

```{r static}
# Static
static <- did_imputation(data = df_het, yname = "dep_var", gname = "g", tname = "year", idname = "unit")

static
```

This is very close to the true treatment effect of `r df_het[treat == 1, mean(te + te_dynamic)]`.

Then, let's estimate an event study did:

```{r event-study}
# Event Study
es <- did_imputation(
  data = df_het, yname = "dep_var", gname = "g",
  tname = "year", idname = "unit",
  # event-study
  horizon = TRUE, pretrends = -5:-1
)

es
```

And plot the results:

```{r plot-es, fig.width=8, fig.height=4, fig.cap="Event-study plot with example data", code_folding=TRUE, layout="l-body-outset"}
pts <- es |>
  as.data.table() |>
  DT(, .(rel_year = term, estimate, std.error)) |>
  DT(, let(
    ci_lower = estimate - 1.96 * std.error,
    ci_upper = estimate + 1.96 * std.error,
    group = "DID Imputation Estimate",
    rel_year = as.numeric(rel_year)
  ))

te_true <- df_het |>
  DT(
    g > 0,
    .(estimate = mean(te + te_dynamic)),
    by = "rel_year"
  ) |>
  DT(, group := "True Effect")

pts <- rbind(pts, te_true, fill = TRUE)

pts <- pts |>
  DT(rel_year >= -5 & rel_year <= 7, ) |> 
  DT(, rel_year := ifelse(group == "DID Imputation Estimate", rel_year - 0.1, rel_year))

max_y <- max(pts$estimate)

ggplot() +
  # 0 effect
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = -0.5, linetype = "dashed") +
  # Confidence Intervals
  geom_linerange(data = pts, mapping = aes(x = rel_year, ymin = ci_lower, ymax = ci_upper), color = "grey30") +
  # Estimates
  geom_point(data = pts, mapping = aes(x = rel_year, y = estimate, color = group), size = 2) +
  # Label
  geom_label(
    data = data.frame(x = -0.5 - 0.1, y = max_y + 0.25, label = "Treatment Starts ▶"), label.size = NA,
    mapping = aes(x = x, y = y, label = label), size = 5.5, hjust = 1, fontface = 2, inherit.aes = FALSE
  ) +
  scale_x_continuous(breaks = -8:8, minor_breaks = NULL) +
  scale_y_continuous(minor_breaks = NULL) +
  scale_color_manual(values = c("DID Imputation Estimate" = "steelblue", "True Effect" = "#b44682")) +
  labs(x = "Relative Time", y = "Estimate", color = NULL, title = NULL) +
  theme_minimal(base_size = 16) +
  theme(legend.position = "bottom")
```


### Comparison to TWFE

```{r plot-compare, fig.width=8, fig.height=4, fig.cap="TWFE and Two-Stage estimates of Event-Study", code_folding=TRUE, layout="l-body-outset"}
# TWFE
twfe <- fixest::feols(dep_var ~ i(rel_year, ref = c(-1, Inf)) | unit + year, data = df_het)

twfe_est <- broom::tidy(twfe)

twfe_est <- twfe_est |>
  DT(grepl("rel_year::", term)) |>
  DT(, .(rel_year = term, estimate, std.error)) |>
  DT(, let(
    rel_year = as.numeric(gsub("rel_year::", "", rel_year)),
    ci_lower = estimate - 1.96 * std.error,
    ci_upper = estimate + 1.96 * std.error,
    group = "TWFE Estimate"
  )) |>
  DT(rel_year >= -5 & rel_year <= 7, ) |>
  DT(, rel_year := rel_year + 0.1)

# Add TWFE Points
both_pts <- rbind(pts, twfe_est, fill = TRUE)

max_y <- max(pts$estimate)

ggplot() +
  # 0 effect
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_vline(xintercept = -0.5, linetype = "dashed") +
  # Confidence Intervals
  geom_linerange(data = both_pts, mapping = aes(x = rel_year, ymin = ci_lower, ymax = ci_upper), color = "grey30") +
  # Estimates
  geom_point(data = both_pts, mapping = aes(x = rel_year, y = estimate, color = group), size = 2) +
  # Label
  geom_label(
    data = data.frame(x = -0.5 - 0.1, y = max_y + 0.25, label = "Treatment Starts ▶"), label.size = NA,
    mapping = aes(x = x, y = y, label = label), size = 5.5, hjust = 1, fontface = 2, inherit.aes = FALSE
  ) +
  scale_x_continuous(breaks = -8:8, minor_breaks = NULL) +
  scale_y_continuous(minor_breaks = NULL) +
  scale_color_manual(values = c("DID Imputation Estimate" = "steelblue", "True Effect" = "#b44682", "TWFE Estimate" = "#82b446")) +
  labs(x = "Relative Time", y = "Estimate", color = NULL, title = NULL) +
  theme_minimal(base_size = 16) +
  theme(legend.position = "bottom")
  
```

